QPLIB: A Library of Quadratic Programming Instances

### 2016-07-29 QPLIB.tex
affiliation updated (please check)

\ifMPC
\author{Fabio Furini \and
        Emiliano Traversi \and
        Alper Atamturk \and
        Pietro Belotti \and
        Pierre Bonami \and
        Sourour Elloumi \and
        Antonio Frangioni \and
        Ambros Gleixner \and
        Nick Gould \and
        Leo Liberti \and
        Andrea Lodi \and
        Ruth Misener \and
        Hans Mittelmann \and
        Nick Sahinidis \and
        Frederic Roupin \and
        Stefan Vigerske \and
        Angelika Wiegele
        }

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France,
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Alper Atamturk \at
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Pierre Bonami \at
%
\and       Sourour Elloumi \at
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
%
\and       Frederic Roupin \at
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, P.O. Box 40 59,50216 Frechen, Germany
           \email{stefan@gams.com}
%
\and       Angelika Wiegele \at
           }

@@

\author{Fabio Furini\\
        LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France\\
        {\tt fabio.furini@dauphine.fr}
%
\and
        Emiliano Traversi\\
        LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France\\
        {\tt emiliano.traversi@lipn.fr}
%
\and    Alper Atamturk\\
%
\and    Pietro Belotti\\
%
\and    Pierre Bonami\\
%
\and    Sourour Elloumi\\
%
\and    Antonio Frangioni\\
        Dipartimento di Informatica, Universit\`a di Pisa\\
        Largo B. Pontecorvo 2, 56127 Pisa, Italy\\
        {\tt frangio@di.unipi.it}
%
\and    Ambros Gleixner\\
%
\and    Nick Gould\\
%
\and    Leo Liberti\\
        CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France\\
        {\tt liberti@lix.polytechnique.fr}
%
\and    Andrea Lodi\\
%
\and    Ruth Misener\\
%
\and    Hans Mittelmann\\
%
\and    Nick Sahinidis\\
%
\and    Frederic Roupin\\
%
\and    Stefan Vigerske\\
%
\and    Angelika Wiegele
        }
\fi

>>>>

\ifMPC
\author{Fabio Furini \and
        Emiliano Traversi \and
        Pietro Belotti \and
        Antonio Frangioni \and
        Ambros Gleixner \and
        Nick Gould \and
        Leo Liberti \and
        Andrea Lodi \and
        Ruth Misener \and
        Hans Mittelmann \and
        Nick Sahinidis \and
        Stefan Vigerske \and
        Angelika Wiegele
        }

\institute{Fabio Furini \at
           LAMSADE, Universit{\'e} Paris Dauphine, 75775 Paris, France.
           \email{fabio.furini@dauphine.fr}
%
\and
           Emiliano Traversi \at
           LIPN, Universit{\'e} de Paris 13, 93430 Villetaneuse, France.
           \email{emiliano.traversi@lipn.fr}
%
\and       Pietro Belotti \at
           Xpress-Optimizer team, FICO, Birmingham UK
           \email{pietrobelotti@fico.com}
%
\and       Antonio Frangioni \at
           Dipartimento di Informatica, Universit\`a di Pisa,
           Largo B. Pontecorvo 2, 56127 Pisa, Italy,
           \email{frangio@di.unipi.it}
%
\and       Ambros Gleixner \at
           Zuse Institute Berlin, Takustr. 7, 14195 Berlin, Germany.
           \email{gleixner@zib.de}
%
\and       Nick Gould \at
           STFC-Rutherford Appleton Laboratory, Chilton, Oxfordshire OX11 0QX,
           England.
           \email{nick.gould@stfc.ac.uk}
%
\and       Leo Liberti \at
           CNRS LIX, Ecole Polytechnique, 91128 Palaiseau, France.
           \email{liberti@lix.polytechnique.fr}
%
\and       Andrea Lodi \at
           Ecole Polytechnique de Montréal, Canada.               \email{andrea.lodi@polymtl.ca}
%
\and       Ruth Misener \at
           Department of Computing,Imperial College London, UK. \email{r.misener@imperial.ac.uk}
%
\and       Hans Mittelmann \at
           School of Mathematical and Statistical Sciences, Arizona State University,      Tempe, AZ 85287-1804, U.S.A.
\email{mittelmann@asu.edu}
%
\and       Nick Sahinidis \at
Chemical Engineering, Carnegie Mellon University, U.S.A. \email{sahinidis@cmu.edu}
%
\and       Stefan Vigerske \at
           GAMS Software GmbH, P.O. Box 40 59,50216 Frechen, Germany.
           \email{stefan@gams.com}
%
\and       Angelika Wiegele \at
Institut für Mathematik, Alpen-Adria-Universität Klagenfurt, Austria.  \email{angelika.wiegele@aau.at}
           }

@@

\author{Fabio Furini\\
%
\and
        Emiliano Traversi\\
%
\and    Pietro Belotti\\
%
\and    Antonio Frangioni\\
%
\and    Ambros Gleixner\\
%
\and    Nick Gould\\
%
\and    Leo Liberti\\
%
\and    Andrea Lodi\\
%
\and    Ruth Misener\\
%
\and    Hans Mittelmann\\
%
\and    Nick Sahinidis\\
%
\and    Stefan Vigerske\\
%
\and    Angelika Wiegele
        }
\fi
